---
title: "NFL Insights"
output: 
  flexdashboard::flex_dashboard:
    orientation: row
    vertical_layout: scroll
    #social: [ "twitter", "github", "menu" ]
    #css: styles/main.css
runtime: shiny
---

```{css}
.chart-stage {
  overflow-y: auto !important;
}
```

```{r setup, include=FALSE}
library(flexdashboard)
library(tidyverse)
library(nflreadr)
library(DT)
library(formattable)
library(ggrepel)
library(scales)
library(ggplot2)
library(nflplotR)
library(sysfonts)
library(showtext)
library(shiny)
library(gt)
library(gtExtras)
library(ggimage)
library(shinyWidgets)
library(nflplotR)

#import font from sysfonts
sysfonts::font_add_google("roboto","roboto")
showtext_auto()

var.season = nflreadr::get_current_season()
var.currentWeek <- nflreadr::get_current_week()
var.plotCaption <- "Chart: @JakobEschler"

var.colorAccent = "#e84393"
var.darkgrey = "#535c68"
var.lightgrey = "#95afc0"
var.red = "#ff7979"

nflTeams <- nflfastR::teams_colors_logos

# local data
#dvoa_teams <- read.csv("data/football-outsiders/fo-dvoa-data.csv")
#epa_teams <- read.csv("data/nfl-adjusted-epa.csv")
#pace_teams <- read.csv("data/football-outsiders/fo-pace-data.csv")

#personnel_groupings_offense <- read.csv("data/nfl-personnel-groupings-offense.csv")
#personnel_groupings_defense <- read.csv("data/nfl-personnel-groupings-defense.csv")

f_create_ranks <- function(df, arrange_by, rank_col_name) {
  df <- df %>% 
    dplyr::arrange({{arrange_by}}) %>% 
    dplyr::mutate({{rank_col_name}} := row_number())
}

players <- nflreadr::load_players() %>% 
  dplyr::filter(status != "RET") %>% 
  dplyr::mutate(player = paste0(nflreadr::clean_player_names(display_name), " (", team_abbr, ", ", position, ")")) %>% 
  dplyr::select(player, gsis_id, gsis_it_id)

pbp <- nflreadr::load_pbp(var.season)
```

# Matchup Overview {data-navmenu="Matchups"}
```{r matchups-globals, echo=FALSE, fig.height=20, message=TRUE, warning=TRUE}
source("R/matchups/matchups-plots.R", local = TRUE)
source("R/matchups/matchups-data.R", local = TRUE)

matchups_renamed <- matchups %>% 
  rename(
    Team = team,
    Opp = opponent,
    "O/U" = total_line,
    Spread = spread_line
    #"Off DVOA" = offense_weighted_dvoa,
    #"Off Pass DVOA" = offense_pass_dvoa,
    #"Off Rush DVOA" = offense_rush_dvoa,
    #"Opp Def DVOA" = defense_weighted_dvoa,
    #"Opp Def Pass DVOA" = defense_pass_dvoa,
    #"Opp Def Rush DVOA" = defense_rush_dvoa,
    #"Off EPA" = adjusted_off_epa,
    #"Off Pass EPA" = adjusted_off_pass_epa,
    #"Off Rush EPA" = adjusted_off_run_epa,
    #"Opp Def EPA" = adjusted_def_epa,
    #"Opp Def Pass EPA" = adjusted_def_pass_epa,
    #"Opp Def Rush EPA" = adjusted_def_run_epa,
    #"Sec / Play Rank" = sec_per_play_rank,
    #"Sec / Play (leading) Rank" = sec_per_play_leading_rank,
    #"Sec / Play (trailing) Rank" = sec_per_play_trailing_rank,
    #"Sec / Play (neutral) Rank" = sec_per_play_neutral_rank
  )
```

## Main {.tabset .tabset-fade}
### Total
```{r matchup-total-comparison, echo=FALSE, fig.height=17}
#output$matchups_total_dvoa <- renderPlot({
#  ggplot2::ggplot(matchups, aes(x = offense_weighted_dvoa, y = defense_weighted_dvoa)) +
#    matchup_annotations(matchups$offense_weighted_dvoa, matchups$defense_weighted_dvoa) +
#    matchup_overview_plot_defaults() +

#    ggplot2::labs(
#      title = "Weighted Total DVOA Matchup",
#      subtitle = "Size indicates spread line (big logo = high favorite)",
#      x = "Weighted Total DVOA - Offense",
#      y = "Weighted Total DVOA - Opponent Defense"
#    )
#}, width = 900, height = 750)

#output$matchups_total_epa <- renderPlot({
#  ggplot2::ggplot(matchups, aes(x = adjusted_off_epa, y = adjusted_def_epa)) +
#    matchup_annotations(matchups$adjusted_off_epa, matchups$adjusted_def_epa) +
#    matchup_overview_plot_defaults() +
#    
#    ggplot2::labs(
#      title = "Adjusted Total EPA Matchup",
#      subtitle = "Size indicates spread line (big logo = high favorite)",
#      x = "Adjusted Total EPA - Offense",
#      y = "Adjusted Total EPA - Opponent Defense"
#    )
#}, width = 900, height = 750)

output$matchup_data <- DT::renderDataTable({
  
  formattable::formattable(
    matchups_renamed %>% 
      select(Team, Opp, "O/U", Spread),
    list(
      "O/U" = formattable::color_tile("#e55039", "#78e08f"),
      "Spread" = formattable::color_tile("#e55039", "#78e08f")
      #"Off DVOA" = formattable::color_tile("#e55039", "#78e08f"),
      #"Off EPA" = formattable::color_tile("#e55039", "#78e08f"),
      #"Off Pass DVOA" = formattable::color_tile("#e55039", "#78e08f"),
      #"Off Pass EPA" = formattable::color_tile("#e55039", "#78e08f"),
      #"Off Rush DVOA" = formattable::color_tile("#e55039", "#78e08f"),
      #"Off Rush EPA" = formattable::color_tile("#e55039", "#78e08f"),
      #"Opp Def DVOA" = formattable::color_tile("#78e08f", "#e55039"),
      #"Opp Def EPA" = formattable::color_tile("#78e08f", "#e55039"),
      #"Opp Def Pass DVOA" = formattable::color_tile("#78e08f", "#e55039"),
      #"Opp Def Pass EPA" = formattable::color_tile("#78e08f", "#e55039"),
      #"Opp Def Rush DVOA" = formattable::color_tile("#78e08f", "#e55039"),
      #"Opp Def Rush EPA" = formattable::color_tile("#78e08f", "#e55039")
    )
  ) %>% 
  formattable::as.datatable(rownames = FALSE, filter = "top", options = list(pageLength = 16, order = list(list(2, 'asc'), list(3, 'asc'))))
})

renderUI({
  fluidRow(
    width = 12,
    #column(
    #  width = 6,
    #  plotOutput("matchups_total_dvoa")
    #),
    #column(
    #  width = 6,
    #  plotOutput("matchups_total_epa")
    #),
    column(
      width = 12,
      div(
        DT::DTOutput("matchup_data"),
        style = "height: 850px;"
      )
    )
  )
})
```

### Passing
```{r matchup-passing-comparison, eval=FALSE, fig.height=18, include=FALSE}
output$matchups_passing_dvoa <- renderPlot({
  ggplot2::ggplot(matchups, aes(x = offense_pass_dvoa, y = defense_pass_dvoa)) +
    matchup_annotations(matchups$offense_pass_dvoa, matchups$defense_pass_dvoa) +
    matchup_overview_plot_defaults() +
    
    ggplot2::labs(
      title = "Weighted Passing DVOA Matchup",
      subtitle = "Size indicates spread line (big logo = high favorite)",
      x = "Weighted Passing DVOA - Offense",
      y = "Weighted Passing DVOA - Opponent Defense"
    )
}, width = 900, height = 750)

output$matchups_passing_epa <- renderPlot({
  ggplot2::ggplot(matchups, aes(x = adjusted_off_pass_epa, y = adjusted_def_pass_epa)) +
    matchup_annotations(matchups$adjusted_off_pass_epa, matchups$adjusted_def_pass_epa) +
    matchup_overview_plot_defaults() +
    
    ggplot2::labs(
      title = "Adjusted Passing EPA Matchup",
      subtitle = "Size indicates spread line (big logo = high favorite)",
      x = "Adjusted Pass EPA - Offense",
      y = "Adjusted Pass EPA - Opponent Defense"
    )
}, width = 900, height = 750)

output$passing_qb_matchups <- DT::renderDataTable({
  DT::datatable(
    matchups_renamed %>% 
      select(Team, Opp, dplyr::starts_with("qb")),
    rownames = F, filter = "top", options = list(pageLength = 16, order = list(4, 'desc'))
  )
})

output$passing_wr_matchups <- DT::renderDataTable({
  DT::datatable(
    matchups_renamed %>% 
      select(Team, Opp, dplyr::starts_with("wr")),
    rownames = F, filter = "top", options = list(pageLength = 16, order = list(4, 'desc'))
  )
})

renderUI({
  fluidRow(
    width = 12,
    column(
      width = 6,
      plotOutput("matchups_passing_dvoa")
    ),
    column(
      width = 6,
      plotOutput("matchups_passing_epa")
    ),
    column(
      width = 6,
      h2("DFS QB Matchups"),
      DT::DTOutput("passing_qb_matchups")
    ),
    column(
      width = 6,
      h2("DFS Receiver Matchups"),
      DT::DTOutput("passing_wr_matchups")
    )
  )
})
```


### Rushing
```{r matchup-rushing-comparison, eval=FALSE, fig.height=10, include=FALSE}
output$matchups_rushing_dvoa <- renderPlot({
  ggplot2::ggplot(matchups, aes(x = offense_rush_dvoa, y = defense_rush_dvoa)) +
    matchup_annotations(matchups$offense_rush_dvoa, matchups$defense_rush_dvoa) +
    matchup_overview_plot_defaults() +
    
    ggplot2::labs(
      title = "Weighted Rushing DVOA Matchup",
      subtitle = "Size indicates spread line (big logo = high favorite)",
      x = "Weighted Rushing DVOA - Offense",
      y = "Weighted Rushing DVOA - Opponent Defense"
    )
}, width = 900, height = 750)

output$matchups_rushing_epa <- renderPlot({
  ggplot2::ggplot(matchups, aes(x = adjusted_off_run_epa, y = adjusted_def_run_epa)) +
    matchup_annotations(matchups$adjusted_off_run_epa, matchups$adjusted_def_run_epa) +
    matchup_overview_plot_defaults() +
    
    ggplot2::labs(
      title = "Adjusted Rushing EPA Matchup",
      subtitle = "Size indicates spread line (big logo = high favorite)",
      x = "Adjusted Rush EPA - Offense",
      y = "Adjusted Rush EPA - Opponent Defense"
    )
}, width = 900, height = 750)

output$passing_rb_matchups <- DT::renderDataTable({
  DT::datatable(
    matchups_renamed %>% 
      select(Team, Opp, dplyr::starts_with("rb")),
    rownames = F, filter = "top", options = list(pageLength = 16, order = list(4, 'desc'))
  )
})

renderUI({
  fluidRow(
    width = 12,
    column(
      width = 6,
      plotOutput("matchups_rushing_dvoa")
    ),
    column(
      width = 6,
      plotOutput("matchups_rushing_epa")
    ),
    column(
      width = 12,
      h2("DFS RB Matchups"),
      DT::DTOutput("passing_rb_matchups")
    ),
  )
})
```



# Singe Matchup {data-navmenu="Matchups"}
## Sidebar {.sidebar}
```{r single-matchup-inputs, eval=FALSE, include=FALSE}
selectInput(
  "selectMatchup",
  "Filter nach Matchup",
  choices = matchups$matchup,
  multiple= F,
  selected = 1
)

matchup <- reactive({
  matchups %>% 
    filter(matchup == input$selectMatchup)
})

renderTable({
  matchups %>% 
    dplyr::filter(matchup == input$selectMatchup) %>% 
    tidyr::gather(category, details, c(weekday, gametime, roof, surface, temp, wind, stadium)) %>%
    dplyr::select(category, details) %>% 
    dplyr::distinct()
})
```

## Main
```{r eval=FALSE, include=FALSE}
single_matchup_charts <- matchups %>% 
  tidyr::gather(offense, offense_value, c(dplyr::starts_with("offense"), dplyr::starts_with("adjusted_off"))) %>% 
  tidyr::gather(defense, defense_value, c(dplyr::starts_with("defense"), dplyr::starts_with("adjusted_def"))) %>% 
  dplyr::mutate(
    category = dplyr::case_when(
      grepl("weighted_dvoa", offense) & grepl("weighted_dvoa", defense) ~ "total_dvoa",
      grepl("pass_dvoa", offense) & grepl("pass_dvoa", defense) ~ "pass_dvoa",
      grepl("rush_dvoa", offense) & grepl("rush_dvoa", defense) ~ "rush_dvoa",
      grepl("adjusted_off_epa", offense) & grepl("adjusted_def_epa", defense) ~ "total_epa",
      grepl("pass_epa", offense) & grepl("pass_epa", defense) ~ "pass_epa",
      grepl("run_epa", offense) & grepl("run_epa", defense) ~ "rush_epa",
    ),
    group = case_when(
      grepl("dvoa", category) ~ "Weighted DVOA",
      grepl("epa", category) ~ "Adjusted EPA"
    )
  ) %>%
  dplyr::filter(!is.na(category))
```

### Offense vs Defense Matchups
```{r single_matchup_total_dvoa, eval=FALSE, fig.height=8, message=FALSE, warning=FALSE, include=FALSE}
renderPlot({
  ggplot2::ggplot(
    subset(
      single_matchup_charts,
      matchup != input$selectMatchup & category %in% c("total_dvoa", "total_epa")),
    aes(x = offense_value, y = defense_value)
  ) +
    matchup_annotations(matchups$offense_weighted_dvoa, matchups$defense_weighted_dvoa) +
    plot_single_matchup() +
    plot_matchup_dvoa_total()
}, width = 500, height = 700)
```

### Offense vs Defense Passing Matchups
```{r single_matchup_pass, eval=FALSE, fig.height=8, message=FALSE, warning=FALSE, include=FALSE}
renderPlot({
  ggplot2::ggplot(
    subset(
      single_matchup_charts,
      matchup != input$selectMatchup & category %in% c("pass_dvoa", "pass_epa")),
    aes(x = offense_value, y = defense_value)
  ) +
    matchup_annotations(matchups$offense_pass_dvoa, matchups$defense_pass_dvoa) +
    plot_single_matchup() +
    plot_matchup_dvoa_pass()
}, width = 500, height = 700)
```

### Offense vs Defense Rushing Matchups
```{r single_matchup_rush, eval=FALSE, fig.height=8, message=FALSE, warning=FALSE, include=FALSE}
renderPlot({
  ggplot2::ggplot(
    subset(
      single_matchup_charts,
      matchup != input$selectMatchup & category %in% c("rush_dvoa", "rush_epa")),
    aes(x = offense_value, y = defense_value)
  ) +
    matchup_annotations(matchups$offense_rush_dvoa, matchups$defense_rush_dvoa) +
    plot_single_matchup() +
    plot_matchup_dvoa_rush()
}, width = 500, height = 700)
```


## Row
```{r injuries, eval=FALSE, fig.height=10, message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}
injuries <- nflreadr::load_injuries() %>% 
  dplyr::rename(status = report_status) %>%
  dplyr::select(gsis_id, week, team, full_name, position, status, practice_primary_injury) %>% 
  rbind(
    nflreadr::load_rosters_weekly() %>% 
      dplyr::filter(status == "R/Injured") %>% 
      dplyr::select(gsis_id, week, team, full_name, position, status) %>% 
      dplyr::mutate(status = "IR"),
    fill = T
  ) %>% 
  dplyr::filter(week == var.currentWeek) %>% 
  dplyr::left_join(
    nflreadr::load_ff_playerids() %>% 
      dplyr::select(gsis_id, pfr_id),
    by = "gsis_id"
  ) %>% 
  dplyr::left_join(
    nflreadr::load_snap_counts() %>% 
      dplyr::group_by(pfr_player_id) %>% 
      dplyr::summarise(across(where(is.numeric), mean, na.rm = T), .groups = "drop") %>% 
      dplyr::select(-week, -season),
    by = c("pfr_id" = "pfr_player_id")
  ) %>% 
  dplyr::mutate(
    snap_pct_avg = case_when(
      position %in% c("C", "FB", "G", "OL", "QB", "RB", "T", "TE", "WR") ~ round(offense_pct, 2),
      position %in% c("CB", "DB", "DE", "DL", "DT", "LB", "S") ~ round(defense_pct, 2)
    )
  ) %>% 
  dplyr::select(-dplyr::ends_with("_id"), -dplyr::ends_with("_snaps"), -dplyr::ends_with("_pct"))
```

### Away
```{r eval=FALSE, include=FALSE}
DT::renderDataTable({
  DT::datatable(
    injuries %>% 
      filter(team == matchup()$away_team) %>% 
      select(-week, -team),
    rownames = F,
    filter = "top",
    options = list(pageLength = 5, order = list(4, 'desc'))
  )
})
```


### Home
```{r eval=FALSE, include=FALSE}
DT::renderDataTable({
  DT::datatable(
    injuries %>% 
      filter(team == matchup()$home_team) %>% 
      select(-week, -team),
    rownames = F,
    filter = "top",
    options = list(pageLength = 5, order = list(4, 'desc'))
  )
})
```


# Matchup History {data-navmenu="History"}
## Sidebar {.sidebar}
```{r matchup-history-sidebar, echo=FALSE, message=TRUE, warning=TRUE}
shiny::textInput(
  "selectNflPlayer",
  "Filter for NFL Player"
)

shinyWidgets::pickerInput(
  "selectNflTeam",
  "Filter for NFL Team",
  choices = setNames(nflTeams$team_abbr, nflTeams$team_name),
  selected = "ARI",
  options = list("actions-box" = TRUE),
  multiple= TRUE
)

shiny::sliderInput(
  "selectPPG",
  "Filter for FPTS/G",
  min = 0,
  max = 30,
  value = 5,
  step = 1,
  ticks = FALSE
)
```

## Main {.tabset .tabset-fade}
```{r matchup-history-globals, message=TRUE, warning=TRUE, include=FALSE}
source("R/players/player-stats.R", local = TRUE)
```

### QB
```{r matchup-history-qb, echo=FALSE, fig.height=10, message=TRUE, warning=TRUE}
output$matchup_history_qb <- gt::render_gt({
    qb_stats %>% 
      dplyr::filter(opponent_team %in% input$selectNflTeam & ppg >= input$selectPPG & grepl(input$selectNflPlayer, player_name)) %>% 
      default_stats_gt() %>% 
      passing_stats_gt() %>% 
      rushing_stats_gt()
})

renderUI({
  fluidRow(
    width = 12,
    column(
      width = 12,
      div(
        gt::gt_output("matchup_history_qb")
      )
    )
  )
})
```

### RB
```{r matchup-history-rb, echo=FALSE, message=TRUE, warning=TRUE}
output$matchup_history_rb <- gt::render_gt({
    skill_stats %>% 
      dplyr::filter(position == "RB" & opponent_team %in% input$selectNflTeam & ppg >= input$selectPPG) %>% 
      default_stats_gt() %>% 
      rushing_stats_gt() %>% 
      receiving_stats_gt()
})

renderUI({
  fluidRow(
    width = 12,
    column(
      width = 12,
      div(
        gt::gt_output("matchup_history_rb")
      )
    )
  )
})
```

### WR
```{r matchup-history-wr, echo=FALSE, message=TRUE, warning=TRUE}
output$matchup_history_wr <- gt::render_gt({
    skill_stats %>% 
      dplyr::filter(position == "WR", opponent_team %in% input$selectNflTeam & ppg >= input$selectPPG) %>% 
      default_stats_gt() %>% 
      receiving_stats_gt() %>% 
      rushing_stats_gt()
})

renderUI({
  fluidRow(
    width = 12,
    column(
      width = 12,
      div(
        gt::gt_output("matchup_history_wr")
      )
    )
  )
})
```

### TE
```{r matchup-history-te, echo=FALSE, message=TRUE, warning=TRUE}
output$matchup_history_te <- gt::render_gt({
    skill_stats %>% 
      dplyr::filter(position == "TE", opponent_team %in% input$selectNflTeam & ppg >= input$selectPPG) %>% 
      default_stats_gt() %>% 
      receiving_stats_gt() %>% 
      rushing_stats_gt()
})

renderUI({
  fluidRow(
    width = 12,
    column(
      width = 12,
      div(
        gt::gt_output("matchup_history_te")
      )
    )
  )
})
```

# Flow Chart {data-navmenu="History"}
## Sidebar {.sidebar}
```{r flow-chart-sidebar, echo=FALSE, message=TRUE, warning=TRUE}
shiny::sliderInput(
  "selectTopFinish",
  "Filter for Top-X Finish",
  min = 1,
  max = 48,
  value = 12,
  step = 1,
  ticks = FALSE
)
```

## Main
```{r flow-chart, echo=FALSE, message=TRUE, warning=TRUE}
source("R/matchups/matchups-data.R", local = TRUE)
source("R/players/player-stats.R", local = TRUE)
source("R/players/flow-chart.R", local = TRUE)

renderUI({
  fluidRow(
    width = 12,
    column(
      width = 12,
      div(
        gt::gt_output("flow_chart")
      )
    )
  )
})
```
